Technical Report

### 2018-03-20 fully-abstract-comp/technical-report.tex
code region change
formatting
First stab at a notion of components

@@

\[
  H^\mathrm{code} \; \ta \; \sigma_\baddr \; \nrcalls \; \nrclosures \; \code \; s \; \hat{W} = \left\{
    \npair{(\code,\code)} \mid
  \begin{multlined}
    \dom(\code) = [\aaddr,\baddr] \tand \sigma_\eaddr = \sigma_\baddr + \nrcalls+\nrclosures - 1 \tand \\
    \code(a) = \seal{\sigma_\baddr,\sigma_\eaddr,\sigma_\baddr}
  \end{multlined}
  \right\}
\]
\lau{19-03-2018: Add the link capability to the above? code in ta?}
\begin{multline*}
  H^\mathrm{code}_\sigma \; \ta \; \sigma_\baddr \; \nrcalls \; \nrclosures \; \code \; s \; \sigma \; \hat{W} = \\
  \begin{array}[t]{l}
\left\{
    \begin{array}{l}
\left. \npair{\arraycolsep=0pt\left(\array{l}\retptrc(\rx,\lin,\baddr,\eaddr,\aaddr'+\calllen - 1),\\((\rx,\lin),\baddr,\eaddr,\aaddr)\endarray\right)} \middle| \right. \\
      \\
      \begin{array}{l}
        \decInstr{\code([a',a' + \calllen-1])} = \overline{\scall{o}{r_1}{r_2}} \tand \\
        \aaddr = \aaddr' + \retoffset \tand \\
        \sigma = \sigma_\baddr + o \tand o < \nrcalls\\
        \lbrack \baddr, \eaddr \rbrack = \dom(\code) \subseteq \ta
      \end{array}
    \end{array}
      \right\} \uplus \\
\left\{
    \begin{array}{l}
\left. \npair{\arraycolsep=0pt\left(\array{l}\retptrd(\baddr,\eaddr),\\((\rw,\linear),\baddr,\eaddr,\aaddr)\endarray\right)} \middle| \right. \\
      \\
      \begin{array}{l}
        \exists r \in \dom(\pwpriv[\xi(\hat{W})]) \ldotp \pwpriv[\xi(\hat{W})](r) \nequal (\stareg[(\ms,\ms)]{\spa}, ((\rx,\lin),\baddr',\eaddr',\aaddr'+\calllen)) \tand \\
        \quad \dom(\ms) = [\baddr,\eaddr] \tand\\
        \quad \decInstr{\code([a',a' + \calllen-1])} = \overline{\scall{o}{r_1}{r_2}} \tand \\
        \quad \sigma = \sigma_\baddr + o \tand o < \nrcalls \tand\\
        \quad a = b-1\tand \\
        \quad \lbrack \baddr', \eaddr' \rbrack = \dom(\code) \subseteq \ta
      \end{array}
    \end{array}
      \right\} \uplus\\
    \left\{
    \begin{array}{l}
\left. \npair{(\vsc, \vsc' )} \middle| \right. \\
      \begin{array}{l}
        \sigma = \sigma_\baddr + o \tand \nrcalls \leq o < \nrcalls + \nrclosures \tand\\
        (\dom(\code) \mathrel{\#} \ta \tand \npair{\vsc,\vsc'} \in \lrv \; W) \tor\\
        (\dom(\code) \subseteq \ta)
      \end{array}
    \end{array}
      \right\}
  \end{array}
\end{multline*}

>>>>

\subsection{Components}
\label{sec:components}

We define a component as follows:
\begin{align*}
  \var{comp} &\mathrel{::=} (\ms_{\mathrm{code}},\ms_{\mathrm{data}},\overline{c}_{\mathrm{import}},\overline{c}_{\mathrm{export}},\sigma_\baddr,\nrcalls,\nrclosures)
\end{align*}

We say that a component is valid ($\vdash \var{comp}$), iff:
\begin{mathpar}
  \inference{}{
    A_{\mathrm{code}},A_{\mathrm{data}},\overline{c_{\mathrm{import}}} \vdash_{\mathrm{comp-value}} z
  }
  \and
  \inference{
    c \in \overline{c_{\mathrm{import}}}
  }{
    A_{\mathrm{code}},A_{\mathrm{data}},A_{\mathrm{own}},\overline{c_{\mathrm{import}}} \vdash_{\mathrm{comp-value}} c
  }
  \and
  \inference{
    [\baddr,\eaddr] \subseteq A_{\mathrm{code}} & \perm \sqsubseteq \rx
  }{
    A_{\mathrm{code}},A_{\mathrm{data}},A_{\mathrm{own}},\overline{c_{\mathrm{import}}} \vdash_{\mathrm{comp-value}} ((\perm,\normal),\baddr,\eaddr,\aaddr)
  }
  \and
  \inference{
    [\baddr,\eaddr] \subseteq A_{\mathrm{data}} & \permbnf \sqsubseteq \rw&
    \lin = \linear \Rightarrow \emptyset \subset [\baddr,\eaddr] \subseteq A_{\mathrm{own}}
  }{
    A_{\mathrm{code}},A_{\mathrm{data}},A_{\mathrm{own}},\overline{c_{\mathrm{import}}} \vdash_{\mathrm{comp-value}} ((\perm,\lin),\baddr,\eaddr,\aaddr)
  }
  \and
  \inference{
    \dom(\ms_{\mathrm{code}}) = [\baddr_{\mathrm{code}},\eaddr_{\mathrm{code}}] &
    \ms_{\mathrm{code}}(\baddr_{\mathrm{code}}) = \seal{\sigma_\baddr,\sigma_\baddr+\nrcalls+\nrclosures-1,\sigma_\baddr}\\
    \forall a \in [\baddr_{\mathrm{code}}+1,\eaddr_{\mathrm{code}}]\ldotp \dom(\ms_{\mathrm{code}}),\dom(\ms_{\mathrm{data}}),\emptyset,\overline{c_{\mathrm{import}}} \vdash_{\mathrm{comp-value}}\ms_{\mathrm{code}}(a)\\
    \exists A_\mathrm{own} : \dom(\ms_{\mathrm{data}}) \rightarrow \powerset{\dom(\ms_{\mathrm{data}})} & \dom(\ms_{\mathrm{data}}) = \biguplus_{a \in \dom(\ms_{\mathrm{data}})} A_{\mathrm{own}}(a) \\
    \forall a \in \dom(\ms_{\mathrm{data}})\ldotp \dom(\ms_{\mathrm{code}}),\dom(\ms_{\mathrm{data}}),A_{\mathrm{own}}(a),\overline{c_{\mathrm{import}}} \vdash_{\mathrm{comp-value}}\ms_{\mathrm{data}}(a)\\
  }{
    \vdash (\ms_{\mathrm{code}},\ms_{\mathrm{data}},\overline{c_{\mathrm{import}}},\overline{c_{\mathrm{export}}},\sigma_\baddr,\nrcalls,\nrclosures)
  }
\end{mathpar}

@@

\[
  H^\mathrm{code} \; \ta \; \sigma_\baddr \; \nrcalls \; \nrclosures \; \code \; s \; \hat{W} = \left\{
    \npair{(\code,\code)} \mid
  \begin{multlined}
    \dom(\code) = [\aaddr,\baddr] \tand \sigma_\eaddr = \sigma_\baddr + \nrcalls+\nrclosures - 1 \tand \\
    \code(a) = \seal{\sigma_\baddr,\sigma_\eaddr,\sigma_\baddr}
  \end{multlined}
  \right\}
\]
\lau{19-03-2018: Add the link capability to the above? code in ta?}
\begin{multline*}
  H^\mathrm{code}_\sigma \; \ta \; \sigma_\baddr \; \nrcalls \; \nrclosures \; \code \; s \; \sigma \; \hat{W} = \\
  \begin{array}[t]{l}
\left\{
    \begin{array}{l}
\left. \npair{\arraycolsep=0pt\left(\array{l}\retptrc(\rx,\lin,\baddr,\eaddr,\aaddr'+\calllen - 1),\\((\rx,\lin),\baddr,\eaddr,\aaddr)\endarray\right)} \middle| \right. \\
      \\
      \begin{array}{l}
        \decInstr{\code([a',a' + \calllen-1])} = \overline{\scall{o}{r_1}{r_2}} \tand \\
        \aaddr = \aaddr' + \retoffset \tand \\
        \sigma = \sigma_\baddr + o \tand o < \nrcalls\\
        \lbrack \baddr, \eaddr \rbrack = \dom(\code) \subseteq \ta
      \end{array}
    \end{array}
      \right\} \uplus \\
\left\{
    \begin{array}{l}
\left. \npair{\arraycolsep=0pt\left(\array{l}\retptrd(\baddr,\eaddr),\\((\rw,\linear),\baddr,\eaddr,\aaddr)\endarray\right)} \middle| \right. \\
      \\
      \begin{array}{l}
        \exists r \in \dom(\pwpriv[\xi(\hat{W})]) \ldotp \pwpriv[\xi(\hat{W})](r) \nequal (\stareg[(\ms,\ms)]{\spa}, ((\rx,\lin),\baddr',\eaddr',\aaddr'+\calllen)) \tand \\
        \quad \dom(\ms) = [\baddr,\eaddr] \tand\\
        \quad \decInstr{\code([a',a' + \calllen-1])} = \overline{\scall{o}{r_1}{r_2}} \tand \\
        \quad \sigma = \sigma_\baddr + o \tand o < \nrcalls \tand\\
        \quad a = b-1\tand \\
        \quad \lbrack \baddr', \eaddr' \rbrack = \dom(\code) \subseteq \ta
      \end{array}
    \end{array}
      \right\} \uplus\\
    \left\{
    \begin{array}{l}
\left. \npair{(\vsc, \vsc' )} \middle| \right. \\
      \begin{array}{l}
        \sigma = \sigma_\baddr + o \tand \nrcalls \leq o < \nrcalls + \nrclosures \tand\\
        (\dom(\code) \mathrel{\#} \ta \tand \npair{(\vsc,\vsc')} \in \lrv \; W) \tor\\
        (\dom(\code) \subseteq \ta \tand \npair{(\vsc,\vsc')} \in \lrvtrusted \; W)
      \end{array}
    \end{array}
      \right\}
  \end{array}
\end{multline*}
